---
title: "Developing Data Product Project"
author: "Charles"
date: "July 4, 2019"
output: ioslides_presentation
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Shiny Presentation

This R Markdown presentation is made interactive using Shiny. The US Personal Expenditure Data underscore different categories of items where data was collected from the period of 1940 till 1960.

The personal Expenditure where data was collected is stated below
 - Food and Tobacco
 - Household Operation
 - Medical and Health
 - Personal Care
 - Private Education
 
The data was generated from the datasets.
 

## Data Summary

```{r, echo= FALSE}
summary(USPersonalExpenditure)

```

## The Personal Expenditure plot

- To View the data for each year of the US Expenditure, From the Expenditure Year  there exist a drop down list where to select the year to view the Boxplot.

- The Boxplot will be displayed with respect to the year selected.


## Reference

- The Application link: https://charlesoke.shinyapps.io/DDP4_US_Personal_Expenditure/

The Source Code of the Assignment: https://github.com/charlesgto/Developing-Data-Product

